Capturing the geometric structure of our experiences and how we remember them

### 2018-07-16 main.tex
removed old lineseg figure

% \title{Capturing the geometric structure of our experiences and how we remember them}
% \title{The fundamental shape of naturalistic experiences is preserved in episodic memory}
\title{Memory dynamics for naturalistic experiences}
\author{Andrew C. Heusser \& Jeremy R. Manning}
% \affiliation{Dartmouth College}

@@

Despite the continuous and (often) gradually changing nature of naturalistic experiences, prior research suggests that our memories for those same experiences may be more descrete and organized around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}. Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience (i.e. ``event boundaries'') may lead to discontinuous in memory \citep{HeusEtal18, BrunEtal18, Radv12}. There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.  However, whether people naturally recount their experiences in a way that is structured around events is not known.

@@

>>>>

\title{Capturing the geometric structure of our experiences and how we remember them}
% \title{The fundamental shape of naturalistic experiences is preserved in episodic memory}
% \title{Memory dynamics for naturalistic experiences}
\author{Andrew C. Heusser \& Jeremy R. Manning}
% \affiliation{Dartmouth College}

@@

% I realize this sticks out and needs to be better integrate into the narrative, but not sure how!
Despite the continuous and (often) gradually changing nature of naturalistic experiences, prior research suggests that our memories for those same experiences may be more descrete and organized around particular ``events'' \citep{Radv12, RadvZack11, BrunEtal18}. Short timescale autocorrelations in the contents of an experience are thought associatively link information in memory, while more drastic changes in perceptual or semantic aspects of an experience (i.e. ``event boundaries'') may lead to discontinuous in memory \citep{HeusEtal18, BrunEtal18, Radv12}. There is now compelling evidence that event boundaries can influence memory organization when learning sequences of items \citep{HeusEtal18, DuBrDava13}, during navigation \citep{BrunEtal18}, and narrative comprehension \citep{ZwaaRadv98, EzzyDava11}.  However, whether people naturally recount their experiences in a way that is structured around events is not known.

@@

\section{Discussion}
\label{sec:discussion}

+ novel way to quantify naturalistic experiences and memories
+ opens the door to studies of how various manipulations (or simply the passage of time) might lead to changes in the structure of naturalistic memories
+ other potential applications - quantifying learning from educational videos, memory assessment/diagnosis of memory disorders and other psychiatric disorders
